\section{OLED display}

For quick access to information and data during testing, we used the OLED
display integrated in the ZedBoard. This display has a resolution of 128x32 pixels
and is controlled through I2C communication.

\section{Code implementation}

For the actual implementation of the OLED display, we used the following
repository:~\cite{OLED:repo} from Michael Mattioli, which provides a simple and
effective way to interface with the display implemented in VHDL and compatible with the ZedBoard.
\paragraph{}

Many of the functions provided by the repository were kept unchanged, while we focused
on implementing new ones to display the information we needed on the screen.
The OLED display is divided into 4 lines, each with a maximum of 16 characters,
and ASCII encoding is used to represent the characters.

\section{Displayed information}

Our audio processing module provides the current frequency of the audio signal. This data is
encoded in Binary-Coded Decimal (BCD) format, where each digit is written as 4-bits,
which guarantee the necessary range from 0 to 9.
The BCD format was chosen because it moves the operational weight of computing each digit
from the OLED writer code, to other modules already tasked with computations.
This allows a quick translation of the input data into an ascii encoded buffer, which will
then be used to print the current frequency.
\paragraph{}

Another information displayed is the note corresponding to the current frequency.
To achieve this we utilize the same data in BCD format and a pre-compiled Look-Up Table (LUT),
containing the various notes in a specific frequency range.
We chose the arbitrary value of 1000 Hz as the upper limit, which is more than enough to
represent any note detected that our system, since the guitar's string can produce frequencies 
around at most 400Hz.
\paragraph{}

The last information displayed on the OLED display is a simple incremental counter,
used for debugging purposes, like ansuring the right refresh rate on the display.
This counter is also passed to the OLED module as a BCD encoded \texttt{std\_logic\_vector}.

